---
title: "meta_script"
author: "Ulisse Gomarasca"
date: "2023-08-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

This document calls all the necessary code scripts that are needed to run the analysis of biodiversity and ecosystem functional properties by Gomarasca et al., submitted.


## Data processing
Preparation of data for the analysis.
Sentinel 2 data was pre-processed and downloaded in Google Earth Engine:
https://code.earthengine.google.com/9274b8930259730af654e6910fd83bae
https://code.earthengine.google.com/c5e4b08a8d0336479bca594279eb04f0


```{r, echo = F}
### Metadata -------------------------------------------------------------------
## Site coordinates for Sentinel 2 cut-outs ----
source("scripts/extract_sites.R")

## Site coordinates, pft classes, and other metadata ----
source("scripts/extract_site_info.R")



### Climatic variables ---------------------------------------------------------
source("scripts/extract_climate_NEON.R")



### Structural variables -------------------------------------------------------
## Vegetation structure ----
source("scripts/extract_structure_NEON.R")


## LAI ----
source("scripts/extract_LAI_GBOV_NEON.R")



### Biodiversity ---------------------------------------------------------------
## Ground biodiversity ----
source("scripts/calculate_site_biodiversity_indices_v06.R")



## Rao's Q + max VIs ----
# Pre-processing of cut-outs in Google Earth Engine by Ulisse Gomarasca, Marco Girardello, Guido Ceccherini
# Calculation of estimatesin python by Javier Pacheco-Labrador
source("scripts/extract_raoq_and_VImax.R")


### Fluxes ---------------------------------------------------------------------
## Extract transpiration at NEON sites ----
# partitioned transpiration and evaporation estimates based on the TEA algorithm by Nelson et al., 2018
source("scripts/extract_TEA_T_NEON.R")


## Extract and calculate missing fluxes from NCAR-NEON product ----
source("scripts/extract_fluxes_NCAR_NEON.R")



### Ecosystem Functional Properties --------------------------------------------
source("scripts/calculate_EFPs.R")



#### Data Merge ----------------------------------------------------------------
source("scripts/data_merge_NEON_4mumin.R")

```


## Analysis

```{r, echo = F, include = F}
### Multimodel Inference -------------------------------------------------------
source("scripts/analyze_multimodel_inference_v11.R")


## Determine site list ----
source("scripts/extract_final_sitelist.R")



### Path Modelling -------------------------------------------------------------
source("scripts/analyze_path_modelling.R")

```


## Plot

```{r, echo = F}
### Figures 2, 3, 4: Choise of RaoQ --------------------------------------------
source("scripts/plot_raoq_vs_gppsat.R") # GPPsat vs RaoQ (Figure 2)
source("scripts/plot_raoq_vs_structure.R") # RaoQ vs structure (Figure 3)
source("scripts/plot_javiers_raoq_simulations.R") # simulated RaoQ (Figure 4)


### Figures 5, S3, S4, S5, S6, S8: Multimodel Inference ------------------------
## Average coefficients
source("scripts/plot_mumin_relimp.R") # plot coeffs from  analyses based on different settings (incl. Figures 5, S3, S4, S5, S6)

## Figure S8: R2 and AICc
source("scripts/plot_mumin_biodiv_evaluation.R") # compare different analyses (Figure S8)



### Figure S7: Path modelling plot ---------------------------------------------
# CURRENTLY MANUAL on Biorender: # plot from output of path modeling (Figure S7)
source("scripts/plot_path_modelling.R") # mock-ups for Figure S7


### Information cards ----------------------------------------------------------
source("scripts/plot_site_info.R")

### Biodiversity exploration ---------------------------------------------------
# source("scripts/compare_ground_satellite.R")
source("scripts/plot_raoq_vs_biodiversity.R") # RaoQ vs biodiversity indeces



```

## Additional materials
Compile supplementary tables and materials.

```{r, echo = F}
### Table S1: Table of sites ---------------------------------------------------
source("scripts/compile_site_table.R")

### Figure S1. Map of NEON sites -----------------------------------------------
source("scripts/plot_neon_map_and_period.R") # map of used sites (Figure S1)

```

## Other materials
Run additional tests.

```{r, echo = F}
### Test correlations ----------------------------------------------------------
source("scripts/analyze_correlations.R")

```